---
title: "Untitled"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Readme

**CLIPflexR** is a R wrapper for the [**CLIP Tool Kit  (CTK)**](https://zhanglab.c2b2.columbia.edu/index.php/CTK_Documentation) and additional functions to call other external libraries into an R environment.

**CLIPflexR** makes use of the **CondaSysReqs** library to install conda dependencies to your machine within a conda environment using the reticulate libraries.

The [**CTK toolkit**](https://zhanglab.c2b2.columbia.edu/index.php/CTK_Documentation) is installed as part of the **CLIPflexR** **install_ctk()** function.

### How to install CLIPflexR
```{r,echo=TRUE,eval=FALSE}
install.packages("devtools")
devtools::install_github("kathrynrozengagnon/CLIPflexR")
devtools::install_github("RockefellerUniversity/CondaSysReqs")
CondaSysReqs::install_CondaSysReqs("CLIPflexR")
CLIPflexR::install_ctk()
```

## Path to Conda tools and CTK/czplib

```{r,echo=TRUE,eval=TRUE}
library(CLIPflexR)
getOption("CLIPflexR.condaEnv")
getOption("CLIPflexR.ctk")
getOption("CLIPflexR.czplib")
```

##See our vignettes for [installing CLIPflexR](https://kathrynrozengagnon.github.io/CLIPflexR/articles/Processing_to_matrix.html/installCliPR.html) or processing CLIP data using [CTK](https://kathrynrozengagnon.github.io/CLIPflexR/articles/StandardandBrdU_Processing_CTK.html) or [CLIPflexR](https://kathrynrozengagnon.github.io/CLIPflexR/articles/Processing_to_matrix.html). You can also mix and match!

##Please bear with us while we update examples and vignettes, more coming soon....

##Report [issues](https://github.com/kathrynrozengagnon/CLIPflexR/issues)
