---
title: "Untitled"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- badges: start -->
  [![R build status](https://github.com/ThomasCarroll/clipr/workflows/R-CMD-check/badge.svg)](https://github.com/ThomasCarroll/clipr/actions)
<!-- badges: end -->


## Readme

**clipR** is a R wrapper for the [**ctk toolkit**](https://zhanglab.c2b2.columbia.edu/index.php/CTK_Documentation) and additional functions to call other external libraries into an R environment.

**clipR** makes use of the **CondaSysReqs** library to install conda dependencies to your machine within a conda environment using the reticulate libraries.

The [**ctk toolkit**](https://zhanglab.c2b2.columbia.edu/index.php/CTK_Documentation) is installed as part of the **clipR** **install_ctk()** function.

### How to install clipR
```{r,echo=TRUE,eval=FALSE}
install.packages("devtools")
devtools::install_github("RockefellerUniversity/clipR")
devtools::install_github("RockefellerUniversity/CondaSysReqs")
CondaSysReqs::install_CondaSysReqs("clipR")
clipR::install_ctk()
```

## Path to Conda tools and Ctk/czplib

```{r,echo=TRUE,eval=TRUE}
library(clipR)
getOption("clipr.condaEnv")
getOption("clipr.ctk")
getOption("clipr.czplib")
```

